Analyzing the Effectiveness of Copyright Law on AI Output in Software Engineering and Future Developments

### 2025-02-15 paper/main.tex
800 words!

\IEEEPARstart{W}{rite} why is important to do this experiment, what background is needed, what technology has been used in this session, you can also talk briefly about what other technology exist but was not used here.
Then explain briefly how the experiment was conducted, what measurements were taken, what technology is used (acquisition system, sensors, software), if calculations were done, what calculations were done, what decisions were made, and what the final result was (explained in a concise way with words).
Writing “good” reports requires much thought, organization and editing but the rewards are
great. Those students who can master good technical writing skills will find greater success and
opportunity as professionals in industry.

% \\
%thesis
For those concerned with the legality of the software they produce, the usage of
AI-generated code should be avoided as their trustworthiness is dubious and
they will become succeptible to copyright law in the near future.

@@

@@

@@

\appendices
\section{Hand calculations (or name your title for appendix subtitle)}
List any extra evidence such as photos of the session, that may help you support your claims.
You can include all hand calculations, extra graphs and plots, simulation results, etc.

@@

% Examples of references:  \\[0.001in]

% Example of data book:\\[0.1in]
% [2] National Operational Amplifiers Databook. Santa Clara: National Semiconductor
% Corporation, 1995 Edition, p. I-54. \\[0.1in]
% Example of textbook: \\[0.1in]
% [3]M. Young, The Technical Writer’s Handbook. Mill Valley, CA: University Science, 1989.\\[0.1in]
% Example of scientific journal paper:\\[0.1in]
% [4] J.W. Smith, L.S. Alans and D.K. Jones, “An operational amplifier approach to
% active cable modeling”, IEEE Transactions on Modeling, vol. 4, no. 2, 1996, pp.
% 128-132.\\[0.1in]
% Example of conference paper proceedings:\\[0.1in]
% [5] J.W. Smith, L.S. Alans and D.K. Jones, “Active cable models for lossy
% transmission line circuits”, in Proc. 1995 IEEE Modeling Symposium, 1996, pp.
% 1086-89.\\[0.1in]

% Example of Internet web page:\\[0.1in]
% [6] Approximate material properties in isotropic materials. Milpitas, CA: Specialty
% Engineering Associates, Inc. web site: www.ultrasonic.com, downloaded Aug. 20,
% 2001.

% List and number all bibliographical 
% references at the end of your paper in {\bf 9 or 10 point} Times, with 10-point interline spacing. When referenced within the text, enclose the citation number in square brackets, for example [1]. \\
% Use IEEE format. Cite any external work that you used (data sheets, text books, Wikipedia articles, . . . ). If you get a formula from a Wikipedia article, you must cite the article, giving the title, the URL, and the data you accessed the article as a minimum. If you copy a figure, not only must you cite the article you copied from, but you must give explicit figure credit in the caption for the figure: This image copied from . . . . If you modify a figure or base your figure on one that has been published elsewhere, you still need to give credit in the caption: This image adapted from . . . .\\[0.1in]

% that's all folks
\end{document}

>>>>

\IEEEPARstart{T}{he} emergence of AI tools has, no doubt, changed many aspects of
how work is approached in many professions, but the greatest impact has been on
software engineering. New tools like Github Copilot, an AI assisted code generation
tool thats usable in many modern code editors today, boasts a 2x speedup of feature
completions and a large boost in productivity for its users \cite{github}. However
accurate those claims may be, theres no doubt that these tools are being used
widely by the developer population, and they arent going away any time soon.

However the code generated by these tools must come from somewhere. Many models
source their training data from the public internet, but not everything in public access
allows for commercial / derivative use. Such models ignore this step,
jumping straight towards using this data with any disregard for copyright protections in place.
While copyright has been slow in the past, there is no doubt the legal systems around the world
will regulate and form precedent for these utilites; Inevitably placing their users
under risk.
% WARN: not sure this is the cleanest way to segue into my theses

\textbf {
  For those concerned with the legality of the software they produce, the usage of
AI-generated code should be avoided as their trustworthiness is dubious and
they will become succeptible to copyright law in the near future.
}

@@

To help understand the context that this paper resides in, below are
lay-person explanations of AI training, Software Licensure, AI tools, and
more.

\subsection{Data Acquisition}

The way AI development labs gather data for their models is
mainly through web scrapers. Web scrapers are programs that access a
immense number of websites, downloading and orgranizing
the all the data they find \cite{Miquido}. The gathered data
is then used to train whichever model they are interested in.

The modern way for a website to prevent a webscraper from
downloading its contents is a file called a `robots.txt`,
that any honest web scraper would look for first, and obey
the rules inside \cite{robots}. The problem with this "trust me" approach
is that a dishonest, or even badly programmed, web scraper
can come along and look past this file and do whatever they please\cite{robots}.

% TODO: could talk about how copilot has access to github, largest source code repo

\subsection{Software Licenses}

While it may come as a suprise to the average person,
even code nowadays has some kind of protection against
copying / un-permitted usage. The mechanism for this
is called a "Software License"\cite{Blackduck}.
The code that these licenses protect is called "source code".
There exist many kinds of licenses, mainly meant for
open use towards the public, but there are a two that are crucial to understand.

\begin{IEEEitemize}
\item Copy Left 
\\
  A "Copy Left" license allows the general public to view and do whatever they
  would like with the source code, but they enforce that any derivative must
  also use the same license. In effect this is a strictly anti-commercial license
  as its quite hard for a buisness to use Copy Left Licensed software as
  anything they produce using that code must have the same
  Copy Left license, and as a result live in the public domain.
  \cite{Blackduck}

\item Proprietary 
\\
A "Proprietary" license are the most restrictive, as they prevent any viewer / user from
copying, modifying, redistrbuting, etc \cite{Blackduck}. They are the defaco type of license for any
commercial code, as they protect code the best, and are legally viable \cite{harvard}.

\end{IEEEitemize}

\subsection{AI-Powered Tools}

The most popular AI tool for developers is Github Copilot, which
helps developers as they write code. Its most important capability, in
the context of this work, is its power to automatically generate code when
you ask. The same capability exists for Claude, OpenAI's models, and others,
where they have the capacity to take a description of what the
user wants, and can write code to perform that task \cite{s_2023}. For example, If we
want to make our own snake game, we could trivially ask a model to
program the snake game.

\subsection{Copyright}

@@

% \\
%thesis

@@

@@

\end{document}
